---
title: "Crime and COVID-19: Reliability of public transport as a proxy for mobility"
author: "Patricio R Estévez-Soto"
date: "June 1, 2021"
output: 
  pdf_document: 
  html_document: 
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=TRUE, echo=TRUE}
require(tidyverse)
require(lubridate)
require(magrittr)
require(broom)
require(ggthemes)

kable <- knitr::kable

adf.test <- tseries::adf.test
white.test <- tseries::white.test

Sys.setenv("TZ"="Europe/London")
require(fable)
require(tsibble)
require(feasts)

## multiprocessing
# require(future)
# 
# plan(multiprocess, workers = 6)


## requires future.apply to be installed

# install.packages("future.apply")

## geom_hex requires hexbin package

# install.packages("hexbin")
# 
# # install.packages("cowplot")
# require(cowplot)
# 
# # load("tmp.Rdata")
# 
# require(scales)

sessionInfo()

```



# Introduction

This document explores the reliability of using public transport passenger numbers as a proxy for mobility.

# Data

Crime data come from Mexico City's Open Data portal and represent criminal investigations undertaken by the City's criminal prosecutor's office. Violence against women (VAW) calls come from a dedicated phone service. Passenger numbers in public transport come from the same open data portal and count Bus Rapid Transit and Metro passengers (as well as a measure combining total passengers of both services). Only total passenger counts were used in the analysis.

```{r import-crime-data}

daily_crime_mobility <- read_csv("https://raw.githubusercontent.com/prestevez/covid-19-crime-mx/master/data/daily_crime_mobility-2020-07-13.csv") %>% as_tsibble()

covid_date <- ymd("2020-02-29")

covid_lockdown <- ymd("2020-03-23")

```


# Data preparation

Observations for the last week of May were discarded to control for the lag in reporting that may affect the most recent figures.

Data were further split into two periods. The "training" data set used to estimate models before the impact of COVID-19 restrictions represent all observations from Jan. 1, 2017 to Feb 28, 2020, the day before the first COVID-19 cases were reported in the country.

```{r data-preparation}

daily_crime_mobility %>%
  filter(fecha < "2020-05-25") %>%
  select(-c(año, mes, diasem)) %>%
  select(date = fecha,
         "All crimes" = all_crimes,
         "Violent robbery" = violent_robbery,
         "Non-violent robbery" = non_violent_robbery,
         "Robbery against residence" = burglary,
         "Serious violent crime (non-sexual)" = violent_crime,
         "Sexual violence" = sex_crime,
         "Domestic violence" = domestic_violence,
         "VAW helpline calls" = calls_vaw,
         "BRT + SCT passengers" = pas_total) %>%
  mutate("BRT + SCT passengers (in millions)" = `BRT + SCT passengers`/1e6) -> daily_crime_mobility

# The names of columns were changed for aesthetic purposes

# split data into periods

daily_crime_mobility_pre_covid <- daily_crime_mobility %>%
  filter(date < covid_date)

daily_crime_mobility_post_covid <-daily_crime_mobility %>%
  filter(date >= covid_date)

daily_crime_mobility_2020 <- daily_crime_mobility %>%
  filter(date >= "2020-01-01")

# create pre/post lockdown subsets

daily_crime_mobility_pre_lockdown <- daily_crime_mobility %>%
  filter(date < covid_lockdown)

daily_crime_mobility_post_lockdown <-daily_crime_mobility %>%
  filter(date >= covid_lockdown)



```

Import Apple Mobility data

```{r apple-mobility}

apple <- read_csv("data/applemobilitytrends-2021-05-02.csv")
daily_crime_mobility %$%
  range(date)[2] -> max_date

apple %>%
  filter(region == "Mexico City") %>%
  select(-geo_type, -region, -alternative_name, -`sub-region`, -country) %>%
  pivot_longer(-transportation_type, names_to = "date") %>%
  mutate(date = ymd(date)) %>%
    filter(date <= max_date) -> apple_cdmx

apple_cdmx %>%
  ggplot(aes(date, value, colour = transportation_type)) +
  geom_line() +
  geom_vline(xintercept = covid_date, linetype = 2) +
  geom_vline(xintercept = covid_lockdown, linetype = 2)


apple_cdmx %$%
  range(date)[1] -> min_date

daily_crime_mobility %>%
  filter(date >= min_date) %>%
  select(date, `BRT + SCT passengers (in millions)`) -> brtsct

brtsct %>%
  filter(date == min_date) %$% `BRT + SCT passengers (in millions)` -> brtsct_index_value

brtsct %>%
  select(date, value = `BRT + SCT passengers (in millions)`) %>%
  mutate(transportation_type = "BRT + SCT") %>%
  select(transportation_type, date, value) %>%
  as_tibble() %>%
  mutate(value = value/brtsct_index_value *  100) %>%
  bind_rows(apple_cdmx) %>%
  ggplot(aes(date, value, colour = transportation_type)) +
  geom_line() +
  geom_vline(xintercept = covid_date, linetype = 2) +
  geom_vline(xintercept = covid_lockdown, linetype = 2)
  

brtsct %>%
  select(date, value = `BRT + SCT passengers (in millions)`) %>%
  mutate(transportation_type = "BRT + SCT") %>%
  select(transportation_type, date, value) %>%
  as_tibble() %>%
  mutate(value = value/brtsct_index_value *  100) %>%
  bind_rows(apple_cdmx) -> mobility_data

```


Now examine the relationship

```{r relationship-mobility}

mobility_data %>%
  pivot_wider(names_from = transportation_type,
              values_from = value) %>%
  select(date, brtsct = `BRT + SCT`, driving, transit, walking) -> mobility_wide

m1 <- lm(brtsct ~ driving, data = mobility_wide)
m2 <- lm(brtsct ~ transit, data = mobility_wide)
m3 <- lm(brtsct ~ walking, data = mobility_wide)

require(texreg)

screenreg(list(m1, m2, m3))

```


```{r arima-mobility}
mobility_wide %>%
  as_tsibble() %>%
  model(driving = ARIMA(brtsct ~ driving),
        transit = ARIMA(brtsct ~ transit),
        walking = ARIMA(brtsct ~ walking)) -> mobility_lm_arima


mobility_lm_arima %>%
  select(driving) %>%
  report

mobility_lm_arima %>%
  select(transit) %>%
  report

mobility_lm_arima %>%
  select(walking) %>%
  report

mobility_wide %>%
  pivot_longer(-c(date, brtsct)) %>%
  ggplot(aes(value, brtsct, colour = name)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~ name)


```




























